---
author: 'Quirin Würschinger'
title: "Social networks of lexical innovation"
output: 
  html_notebook: 
    toc: yes
---

# Packages

```{r include=FALSE}
# library(readr)
# library(dplyr)
# library(lubridate)
source('src/load-data.R')
source('src/postproc.R')
source('src/uses.R')
source('src/users.R')
source('src/sna.R')

library(corrr)
```

# Case studies

## Load data

```{r include=FALSE}
corpus <- '/Volumes/qjd/twint/'
lemma <- 'deep learning'

tweets <- load_data(corpus, lemma)
tweets <- postproc(tweets)
```


## Check tweets

```{r}
tweets %>%
  select(tweet) %>%
  slice(., sample(1:n()))
```


## Usage intensity

```{r}
uses <- get_uses(tweets)
uses_tot <- get_uses_tot(uses)
age = get_age(uses)
coef_var <- get_coef_var(uses)
mean_date <- get_mean_date(uses)
max_date <- get_max_date(uses)
uses_month <- conv_uses_month(uses)
uses_plt <- plt_uses(uses_month, lemma, mean_date, max_date)
uses_plt
```


### Advanced (S-curve)

Candidates

* deep learning
* artificial intelligence
* ghosting
* co-working


# Comparative analyses

```{r include=FALSE}
df_comp <- read_csv('out/df_comp.csv')
```

## Processing status

```{r}
df_comp %>%
  select(LEMMA, SUBSET, STAMP) %>%
  filter(SUBSET == 'full') %>%
  mutate(STAMP = as_datetime(STAMP)) %>%
  arrange(desc(STAMP))
```



## Degree centrality

### Overall

#### List

```{r}
df_comp %>%
  select(LEMMA, SUBSET, USES, CENT_DEGREE) %>%
  filter(SUBSET == 'full') %>%
  # filter(USES > 20000) %>%
  arrange((CENT_DEGREE))
```


#### Plot

```{r}
plt <- df_comp %>%
  select(LEMMA, SUBSET, USES, CENT_DEGREE) %>%
  filter(SUBSET == 'full') %>%
  arrange((CENT_DEGREE)) %>%
  ggplot(., aes(x=CENT_DEGREE, y=reorder(LEMMA, CENT_DEGREE))) +
    geom_point() +
    scale_x_continuous(trans='log')
ggplotly(plt)
```


### Over time

#### Single lemma

```{r}
df_comp %>%
  filter(LEMMA == 'artificial intelligence') %>%
  select(SUBSET, CENT_DEGREE) %>%
  mutate(SUBSET = factor(SUBSET, levels=c('first', 'mean', 'max', 'last'))) %>%
  ggplot(., aes(x=SUBSET, y=CENT_DEGREE)) +
    geom_point()
```

#### Across all lemmas

```{r}
df_comp %>%
  filter(SUBSET != 'full') %>%
  group_by(SUBSET) %>%
  summarize(CENT_AVG = mean(CENT_DEGREE)) %>%
  mutate(SUBSET = factor(SUBSET, levels=c('first', 'mean', 'max', 'last'))) %>%
  ggplot(., aes(x=SUBSET, y=CENT_AVG)) +
    geom_point()
```


# Usage intensity vs. network characteristics

## Uses vs. degree centralization

### Plot

```{r}
plt <- df_comp %>%
  filter(SUBSET == 'full') %>%
  select(LEMMA, CENT_DEGREE, USES) %>%
  ggplot(., aes(x=CENT_DEGREE, y=USES)) +
    geom_text(aes(label=LEMMA)) + 
    scale_y_continuous(trans='log') + 
    scale_x_continuous(trans='log')
ggplotly(plt)
```

### Correlation

```{r}
df_comp %>%
  filter(SUBSET == 'full') %>%
  select(CENT_DEGREE, USES) %>%
  correlate()
```


## Degree centrality vs. communities

### Correlation

```{r}
df_comp %>%
  filter(SUBSET == 'last') %>%
  select(CENT_DEGREE, COMMUNITIES) %>%
  mutate(COMMUNITIES = as.numeric(COMMUNITIES)) %>%
  correlate()
```


### Plot

```{r}
df_comp %>%
  filter(SUBSET == 'last') %>%
  select(LEMMA, CENT_DEGREE, COMMUNITIES) %>%
  ggplot(., aes(x=CENT_DEGREE, y=as.numeric(COMMUNITIES))) +
    geom_text(aes(label=LEMMA)) +
    scale_x_continuous(trans='log')
```



## Uses vs. users

### Plot

```{r}
plt <- df_comp %>%
  filter(SUBSET == 'full') %>%
  select(LEMMA, USES, USERS) %>%
  ggplot(., aes(x=USERS, y=USES)) +
    geom_text(aes(label=LEMMA)) +
    scale_x_continuous(trans='log') + 
    scale_y_continuous(trans='log')
ggplotly(plt)
```

### Correlation

```{r}
df_comp %>%
  filter(SUBSET == 'full') %>%
  select(USES, USERS) %>%
  correlate()
```


## Coefficient of variation

```{r}
df_comp %>%
  filter(SUBSET == 'full') %>%
  select(LEMMA, COEF_VAR) %>%
  arrange(desc(COEF_VAR))
```


# COEF_VAR vs. CENT

```{r}
df_comp %>%
  filter(SUBSET == 'full') %>%
  select(LEMMA, COEF_VAR, CENT_DEGREE) %>%
  ggplot(., aes(y=COEF_VAR, x=CENT_DEGREE)) +
    geom_text(aes(label=LEMMA)) +
    scale_y_continuous(trans='log')
```


# Other network metrics

```{r}
df_comp %>%
  filter(SUBSET == 'last') %>%
  View()
```

#


# Correlations

```{r}
library(Hmisc)

df_corr <- df_comp %>%
  # filter(SUBSET == 'last') %>%
  select(-c(LEMMA, SUBSET, NET_WINDOW_DATES, SKIP, STAMP, NROWS))
  # select(-c(USERS, AGE)) %>%
  # mutate(FOCUS = USES) %>%
  # focus(FOCUS) %>%
  # ggplot(., aes(reorder(rowname, FOCUS), FOCUS)) +
    # geom_col() +
    # coord_flip()
  # rearrange() %>%
  # shave() %>%
  # rplot()
  # network_plot(min_cor=.5) %>%

  
```

```{r}

df_corr_full <- df_comp %>%
  filter(SUBSET == 'full') %>%
  select(-c(LEMMA, SUBSET, NET_WINDOW_DATES, SKIP, STAMP, NROWS))
  
cor.test(df_corr_full$USES, df_corr_full$CENT_DEGREE)
```

  