---
title: "Social networks of lexical innovation"
author: "Quirin Würschinger"
output:
  github_document:
    toc: yes
    toc_depth: 1
---

# Load code

## Packages

```{r echo=TRUE, results='hide'}
library(corrr)
library(tidyr)
library(magrittr)
library(forcats)
library(broom)
```


## Custom scripts

```{r echo=TRUE, results='hide'}
source('src/load-data.R') 
source('src/postproc.R')
source('src/uses.R')
source('src/users.R')
source('src/sna.R')
source('src/analysis.R')
```


# Variables

```{r echo=TRUE, results='hide'}
corpus <- '/Volumes/qjd/twint/'

subsetting = 'time'
diff_start_method <- 'edges'
diff_start_limit <- 3

cases <- c(
  'upskill',
  'hyperlocal',
  'solopreneur',
  'alt-right',
  'alt-left',
  'poppygate'
  )
```


# Load data

Load the aggregate data resulting from `processing.R`:

# ```{r echo=TRUE, results='hide'}
```{r}
if (exists('df_comp') == FALSE) {
  df_comp <- read_df_comp(f_path='out/df_comp.csv')
}
```

Filter records to relevant subsetting method:

```{r echo=TRUE, results='hide'}
df_comp %<>% 
  filter(
    SKIP != TRUE,
    SUBSETTING == subsetting,
  )
```


# Table 1: Overall usage frequency

```{r}
df_stats <- tibble(
  STAT = c('MIN', 'MAX', 'MEAN', 'MEDIAN'),
  VALUE = c(min(df_comp$USES_TOT), max(df_comp$USES_TOT), mean(df_comp$USES_TOT), median(df_comp$USES_TOT))
  )

exs_min <- df_comp %>% 
  filter(SUBSET == 'full') %>%
  arrange(USES_TOT) %>%
  select(LEMMA, USES_TOT) %>%
  top_n(-6, USES_TOT) %>%
  mutate(GROUP = 'min')
  
exs_max <- df_comp %>% 
  filter(SUBSET == 'full') %>%
  arrange(desc(USES_TOT)) %>%
  select(LEMMA, USES_TOT) %>%
  top_n(6, USES_TOT) %>%
  mutate(GROUP = 'max')

exs_median <- df_comp %>% 
  filter(SUBSET == 'full') %>%
  arrange(desc(USES_TOT)) %>%
  filter(USES_TOT <= df_stats %>% filter(STAT == 'MEDIAN') %>% pull(VALUE)) %>%
  select(LEMMA, USES_TOT) %>%
  top_n(6, USES_TOT) %>%
  mutate(GROUP = 'median')

exs_mean <- df_comp %>% 
  filter(SUBSET == 'full') %>%
  arrange(USES_TOT) %>%
  filter(USES_TOT >= df_stats %>% filter(STAT == 'MEAN') %>% pull(VALUE)) %>%
  select(LEMMA, USES_TOT) %>%
  top_n(-6, USES_TOT) %>%
  mutate(GROUP = 'mean')

exs_cases <- df_comp %>%
  filter(SUBSET == 'full') %>%
  arrange(desc(USES_TOT)) %>%
  filter(LEMMA %in% cases) %>%
  select(LEMMA, USES_TOT) %>%
  mutate(GROUP = 'case')

df_examples <- bind_rows(exs_min, exs_max, exs_median, exs_mean, exs_cases)

df_examples %<>% 
  mutate(GROUP = factor(GROUP, c('min', 'median', 'mean', 'max', 'case'))) %>%
  arrange(GROUP)

df_examples
```


# Figure 1: Cumulative increase in usage frequency (case studies)

This code cannot be executed since it requires the original tweet data.

```{r eval=FALSE}
uses_cum <- NULL
# lemmas_done <- uses_cum %>% distinct(LEMMA) %>% pull()
for (lemma in cases) {
  tweets <- load_data(corpus, lemma)
  tweets <- postproc(tweets)
  tweets <- filter_tweets(tweets)
  uses <- get_uses(tweets)
  uses_month <- bin_uses(uses, 'month')
  uses_month %<>%
   mutate(LEMMA = lemma) %>%
   mutate(USES_CUM = cumsum(USES))
  uses_cum <- bind_rows(uses_cum, uses_month)
}

uses_cum %>%
  mutate(LEMMA = fct_reorder(LEMMA, USES_CUM, max, .desc=TRUE)) %>%
  filter(LEMMA %in% c(cases)) %>%
  filter(LEMMA != 'alt-right') %>%
  ggplot(data=., aes(x=DATE, y=USES_CUM)) +
    geom_line(aes(color=LEMMA, linetype=LEMMA)) +
    scale_y_continuous('cumulative usage frequency', labels=scales::comma) +
    scale_x_date('') +
    scale_color_discrete('lemma') +
    scale_linetype_discrete(guide=FALSE)
```


# Figure 2: Temporal dynamics in usage frequency

These plots cannot be generated here, since the orginal tweets dataset would be required. The plots were created for all lexemes during the data processing. The code for creating the plots can be in `scr/processing.R`.


# Table 2: Coefficients of variation

```{r}
coef_var <- df_comp %>%
  filter(
    SUBSET == 'full',
    AGE >= 365,
    USES_TOT >= 2000,
    ) %>%
  select(LEMMA, COEF_VAR)

coef_var_cases <- coef_var %>%
  filter(LEMMA %in% cases) %>%
  arrange(COEF_VAR)

coef_var_high <- coef_var %>%
  arrange(desc(COEF_VAR)) %>%
  top_n(6, COEF_VAR)

coef_var_low <- coef_var %>%
  arrange((COEF_VAR)) %>%
  top_n(-6, COEF_VAR)


print(coef_var_cases)
print(coef_var_high)
print(coef_var_low)
```


# Table 3: Degree centrality scores

```{r}
cent_deg <-  df_comp %>%
  select(LEMMA, SUBSET, CENT_DEGREE) %>%
  filter(SUBSET == 'four') %>%
  select(-SUBSET) %>%
  arrange(CENT_DEGREE)

cent_deg_cases <- cent_deg %>%
  filter(LEMMA %in% cases)

cent_deg_low <- cent_deg %>%
  top_n(-6, CENT_DEGREE)

cent_deg_high <- cent_deg %>%
  top_n(6, CENT_DEGREE) %>%
  arrange(desc(CENT_DEGREE))

print(cent_deg_cases)
print(cent_deg_low)
print(cent_deg_high)
```



# Figure 4: Degrees of diffusion for case studies in Subset 4

The network graphs are not presented here since they were generated using `Gephi`. The code for generating the network graphs and exporting the edges and nodes of the network for visualisation in `Gephi` can be found in `src/sna.R`.


# Figure 5: Pathways of social diffusion

```{r}
df_comp %>%
  select(LEMMA, SUBSET, CENT_DEGREE) %>%
  filter(
    SUBSET != 'full',
    LEMMA %in% c(cases)
  ) %>%
  ggplot(., aes(x=SUBSET, y=CENT_DEGREE)) +
    geom_point(aes(group=LEMMA, color=LEMMA)) +
    geom_line(aes(group=LEMMA, color=LEMMA, linetype=LEMMA)) +
    guides(group=TRUE) +
    scale_y_continuous('degree centrality') +
    scale_x_discrete('subset') +
    scale_color_discrete('lemma') +
    scale_linetype_discrete(guide=FALSE)
```


# Figure 6: Social diffusion over time for _hyperlocal_.

The network graphs are not presented here since they were generated using `Gephi`. The code for generating the network graphs and exporting the edges and nodes of the network for visualisation in `Gephi` can be found in `src/sna.R`.


# Table 4: Correlations for 'degree centrality'

## Log-transformation and centering

```{r}
df_comp <- df_comp %>%
  mutate(CENT_DEGREE_LOG_CENT = scale(log(CENT_DEGREE)), scale=FALSE) %>%
  mutate(USES_LOG_CENT = scale(log(USES)), scale=FALSE) %>%
  mutate(USES_TOT_LOG_CENT = scale(log(USES_TOT)), scale=FALSE) %>%
  mutate(AGE_LOG_CENT = scale(log(AGE)), scale=FALSE) %>%
  mutate(COEF_VAR_LOG_CENT = scale(log(COEF_VAR)), scale=FALSE)
```


## Correlation tests: `CENT_DEGREE` X ...

### with FREQUENCY

```{r}
df_comp %>%
  filter(SUBSET != 'full') %>%
  do(tidy(cor.test(df_comp$CENT_DEGREE_LOG_CENT, df_comp$USES_LOG_CENT,  method='spearman')))
```


### with AGE

```{r}
df_comp %>%
  filter(SUBSET == 'full') %>%
  do(tidy((cor.test(.$CENT_DEGREE_LOG_CENT, .$AGE_LOG_CENT,  method='spearman'))))
```


### with VOLATILITY

```{r}
df_comp %>%
  filter(SUBSET != 'full') %>%
  do(tidy(cor.test(.$CENT_DEGREE_LOG_CENT, .$COEF_VAR_LOG_CENT, method='spearman')))
```


## 'predictive' correlation

Correlation between

- `CENT_DEGREE` in Subset 1 with
- overall usage frequency

```{r}
df_comp %>%
  filter(SUBSET == 'one') %>%
  do(tidy((cor.test(.$CENT_DEGREE_LOG_CENT, .$USES_TOT_LOG_CENT,  method='spearman'))))
```



# Figure 7: Relationship between FREQUENCY and CENTRALITY

## Full sample

```{r}
df_comp %>%
  filter(SUBSET == 'four') %>%
  select(LEMMA, CENT_DEGREE, USES_TOT, USES, EDGES) %>%
  ggplot(., aes(x=CENT_DEGREE, y=USES_TOT)) +
    geom_text(aes(label=LEMMA), hjust=-0.1, vjust=-0.1) + 
    scale_y_continuous(
      'usage frequency (log)', 
      trans='log',
      labels=function(x)round(x,-3)
      ) +
    scale_x_continuous(
      'degree centralization (log)',
      trans='log',
      labels=function(x)round(x,3)
      )
```


## Case studies

```{r}
subset <- 'four'

df_cases <- df_comp %>%
  filter(
    SUBSET == subset,
    LEMMA %in% c(cases),
    !LEMMA %in% c(
      'upskill',
      'poppygate'
      )
    )

cases_freq_min <- df_cases %>%
  dplyr::summarise(USES_MIN = min(USES_TOT)) %>%
  pull(USES_MIN)
  
cases_freq_max <- df_cases %>%
  dplyr::summarise(USES_MAX = max(USES_TOT)) %>%
  pull(USES_MAX)

df_comp %>%
  filter(
    SUBSET == subset,
    USES_TOT >= cases_freq_min,
    USES_TOT <= cases_freq_max,
    # filter specific lexemes to prevent overlap
    !LEMMA %in% c('big dick energy', 'slut shaming', 'cuckold', 'shareable', 'Brexiteer', 'incel', 'dashcam', 'refugee crisis')
    ) %>%
  select(LEMMA, CENT_DEGREE, USES_TOT, USES, EDGES) %>%
  ggplot(., aes(x=CENT_DEGREE, y=USES_TOT)) +
    geom_text(aes(label=LEMMA), color='black', hjust=.4, vjust=-.6) + 
    geom_text(data=df_cases, aes(label=LEMMA), color='blue', hjust=.4, vjust=-.6) +
    geom_point() + 
    scale_y_continuous(
      'usage frequency (log)', 
      trans='log',
      labels=function(x)round(x,-3)
      ) +
    scale_x_continuous(
      'degree centralization (log)',
      trans='log',
      labels=function(x)round(x,3)
      )
```